---
title: "Ashley's Garmin Dashboard"
author: "Ashley Lowe"
date: "12/13/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
Activities <- read_csv("~/workspace/garmin/Activities.csv")
library(ggplot2)
library(dplyr)
library(dygraphs)
library(xts)
library(knitr)
library(stargazer)

Activities$date<-as.POSIXct(Activities$Date,format="%m/%d/%y %H:%M")

Activities$avgpace<-as.numeric(Activities$`Avg Pace`)
linear<-lm(log(`avgpace`)~Distance+`Avg Run Cadence`+`Avg HR`+`Avg Stride Length`, data = Activities)

```

### Garmin Dashboard Using R Markdown
I am testing out the various ways I can make a dashboard with R, JS and Python.

##Regressional Anaylsis 
Regressional Anaylsis shows me that :  


* The Econometric model explains 86% of the data.  
* Distance is not significant in explaining my overall average pace.  
* Average Run Cadence is significant in my overall average pace. It suggests that for each unit my cadence increase my average pace decreases by .9%  
* My Average Heart is significant in understanding my overal average pace. It suggests that for unit increase in average heart per minute increases my average pace decreases by .1%.  
* The Average Stride Length is also significant in my overall average pace. This unit is calculated as a precentage. Therefore, for each 1% increase in Average Stride Length my average pace increases by 39.5%.  

```{r results = "asis"}


stargazer::stargazer(linear, type = "html", 
          title = "Regression results", 
          header = FALSE,
          single.row = TRUE)

```



##Graphical Exploration

### Average Pace with a Predicted Fit

This graph shows my average pace since I got my garmin in 2018. Soon after getting the watch I broke my leg and was in a cast. I stopped running regularly.

When Covid-19 shutdowns began in March 2020 I decided to start a build in training schedule in Garmins App. II completed both a Marathon Training and a half marathon training. 

```{r }
p <- ggplot(Activities, aes(x=date, y=`Avg Pace`)) +
     geom_line(color = "#00AFBB", size = .5) + 
     xlab("") +  theme_minimal()
p + stat_smooth( color = "#FC4E07", fill = "#FC4E07",)+labs(title="Average Pace Speed in Minutes with Predicted Linear Fit",
        x ="Since Buying Garmin Watch 2018")
```





```{r }
p <- ggplot(Activities, aes(x=date, y=`Avg Run Cadence`)) +
     geom_line(color = "#8142f5", size = .5) + 
     xlab("") +  theme_minimal()
p + stat_smooth( color = "#FC4E07", fill = "#FC4E07",)+labs(title="Average Run Cadence with Predicted Linear Fit",
        x ="Since Buying Garmin Watch 2018")
```




```{r }
p <- ggplot(Activities, aes(x=date, y=`Avg HR`)) +
     geom_line(color = "#FC4E07", size = .5) + 
     xlab("") +  theme_minimal()
p + stat_smooth( color = "#326fa8", fill = "#327da8",)+labs(title="Average HR with Predicted Linear Fit",
        x ="Since Buying Garmin Watch 2018")
```

```{r }
p <- ggplot(Activities, aes(x=date, y=`Avg Stride Length`)) +
     geom_line(color = "#48a832", size = .5) + 
     xlab("") +  theme_minimal()
p + stat_smooth( color = "#FC4E07", fill = "#FC4E07",)+labs(title="Average HR with Predicted Linear Fit",
        x ="Since Buying Garmin Watch 2018")
```


### Summary statistics table 


```{r }
summary(Activities)
```
